Fractional Decomposition Trees: A tool for studying mixed-integer-program integrality gaps

### 2018-11-21 IPCO format/binaryFDT.tex
binaryFDT updated

@@

In this section we present the fractional decomposition tree (FDT) algorithm and prove its correctness.

Consider a formulation instance $I=(A,G,b)$. Define sets $S(I)$ and $P(I)$ as in (\ref{S'}) and (\ref{P'}), respectively. Also assume we are given a point $(x^*,y^*)\in P(I)$. For instance, $(x^*,y^*)$ can be the optimal solution of minimizing a cost function $cx$ over set $P$, which provides a lower bound on $\min_{(x,y)\in S(I)} cx$. In this section, we prove Theorem \ref{binaryFDT}.  One key ingredient in proving Theorem \ref{binaryFDT} is Theorem \ref{domtoIP} that we will also prove in this section.

Although the theoretical worst-case upper bound on $C$ in the statement of Theorem \ref{binaryFDT} can be very large, we will show that in practice $C$ can be really small and hence FDT can provide good LP-based approximation algorithms in many cases. We also remark that if $g_I=1$, then the algorithm will give an exact decomposition of any feasible solution.  In the remainder of this section we explain the FDT algorithm and prove Theorem \ref{binaryFDT}. For simplicity in the notation we denote $P(I),S(I),$ and $g_I$ with $P,S,$ and $g$, respectively. Let $t=|\spp(x^*)|$. We assume without loss of generality that $\spp(x^*)= \{1,\ldots,t\}$.

The FDT algorithm grows a tree similar to the classic branch-and-bound search tree for integer programs. Each node represents a partially integral vector $(\bar{x},\bar{y})$ in $\dom(P)$ together with a multiplier $\bar{\lambda}$. The solutions contained in the nodes of the tree become progressively more integral at each level. In each level of the tree, the algorithm maintain a conic combination of points with the properties mentioned above. Leaves of the FDT tree contain solutions with integer values for all the $x$ variables that dominate a point in $P$. We will later see how we can turn these into points in $S$. We begin with the following lemmas that show how the FDT algorithm branches on a variable.
\begin{lemma}\label{LPClemma}
	Given $(x',y')\in \dom(P)$ and $\ell\in \{1,\ldots,n\}$, we can find in polynomial time vectors $(\hat{x}^0,\hat{y}^0),(\hat{x}^1,\hat{y}^1)$ and scalars $\gamma_0,\gamma_1 \in [0,1]$ such that: (i) $\gamma_0 + \gamma_1  \geq \frac{ 1}{g}$, (ii) $(\hat{x}^0,\hat{y}^0)$ and $(\hat{x}^1,\hat{y}^1)$ are in  $ P$
		,(iii) $\hat{x}^0_\ell=0$ and $\hat{x}^1_\ell=1$, (iv) $\gamma_0 \hat{x}^0 + \gamma_1\hat{x}^1 \leq x'$.
\end{lemma}

@@

Let us define the FDT algorithm more formally. The algorithm maintains nodes $L_i$ in iteration $i$ of the algorithm. The nodes in $L_i$ correspond to the nodes in level $L_i$ of the FDT tree. The points in the leaves of the FDT tree, $L_t$, are points in $\dom(P)$ and are integral for all integer variables.

@@

	Notice that $\theta = \gamma$ is in fact a feasible solution to $\prun(L')$. Let $\theta^*$ be the optimal vertex point solution to this LP. Since the problem is in $\bbbr^{2k}$,  $\theta^*$ has to satisfy $2k$ linearly independent constraints at equality. However, there are only $t$ constraints of type (\ref{packs}). Therefore, there are at most $t$ coordinates of $\theta^*_j$ that are non-zero. We claim that $L_{i+1}$ which consists of $(x^j,y^j)$ for $j=1,\ldots,2k$ and their corresponding multipliers $\theta^*_j$ satisfy the properties in the statement of the lemma. Notice that, we can discard the nodes in $L_{i+1}$ that have $\theta^*_j=0$, so $|L_{i+1}| \leq t$. Also, since $\theta^*$ is optimal and $\gamma$ is feasible for $\prun(L')$, we have $\sum_{j=1}^{k} \theta^*_j \geq \sum_{j=1}^{2k}\gamma_j \geq \frac{1}{g^{i+1}}$. 
\end{proof}
The leaves of the FDT tree,  $L_t$, have the property that every solution $(x,y)$ in $L_t$ has $x\in\{0,1\}^n$ and $(x,y)\in \dom(P)$. Our goal to now replace these leaves solutions in $\dom(P)$ with solutions in $S$. To this end, we need to reduce some variables with value of 1 into variables of value 0 and obtain feasibility in the meantime. We introduce a procedure that given a  point $(x,y)\in \dom(P)$ with $x\in \{0,1\}^n$ outputs a point $z\leq x$ with $z\in \{0,1\}^n$ such that $(z,w)$ is in $S$ for some vector $w\in \bbbr^p$.

The algorithm ``fixes" the variables iteratively, from $x_1$ to $x_t$. Suppose we run the algorithm for $\ell\in \{0,\ldots,t-1\}$ iterations and we have $(x^{(\ell)},y^{(\ell)})\in \dom(P)$  such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,t$. Now consider the following linear program. The variables of this LP are the $z\in \bbbr^n$ variables and $w\in \bbbr^p$.
\begin{align}
	\DOMtoS(x^{(\ell)})\quad\quad& \min\quad \;z_{\ell+1}\\
	&\;\text{s.t.} \quad \;\;Az+ Gw\geq b \\
	&\;{\color{white}{\text{s.t.}} }\quad \;\; \; z_j = x^{(\ell)}_j \quad \; j =1,\ldots, \ell\\
	&\;{\color{white}{\text{s.t.}} }\quad \; \;\; z_j \leq x^{(\ell)}_j \quad \; j = \ell+1,\ldots,n\\
	&\;{\color{white}{\text{s.t.}} }\quad \; \;\; z\;\geq 0
\end{align}

If the optimal value to $\DOMtoS(x^{(\ell)})$ is 0, then let $x^{(\ell+1)}_{\ell+1} = 0$. Otherwise if the optimal value is strictly positive let $x^{(\ell+1)}_{\ell+1} = 1$. Let $x^{(\ell+1)}_j = x^{(\ell)}_j$ for $j\in \{1,\ldots,n\}\setminus \{\ell+1\}$. This procedure is the DomToIP algorithm.
\iffalse{
\begin{algorithm}[H]
	\KwIn{$(x,y)\in \dom(S)$}
	\KwOut{$(x^{(t)},y^{(t)}) \in S$, $x^{(t)}\leq x$}
	$x^{(0)}\leftarrow x$\\
	\For{$\ell = 0$ \textbf{to} $t-1$}{
		$x^{(\ell+1)} \leftarrow x^{(\ell)}$\\
		$\eta \leftarrow$ optimal value of $ \DOMtoS(x^{(\ell)})$\\
		$y^{(\ell+1)}\leftarrow$ optimal solution for $w$ variables in $ \DOMtoS(x^{(\ell)})$\\
		\eIf{$\eta = 0$}{
			$x^{(\ell+1)}_{\ell+1} \leftarrow 0$\
		}{
			$x^{(\ell+1)}_{\ell+1} \leftarrow 1$
		}
	}
	\label{domtoIPalg}
	\caption{The DomToIP algorithm}
\end{algorithm}
}\fi
The following lemma proves Theorem \ref{domtoIP}.
\begin{lemma}
	Given $(x,y)\in \dom(P)$, DomToIP algorithm correctly finds $(x^{(t)},y^{(t)})\in S$ in polynomial time.
\end{lemma}

\begin{proof}
	First, we need to show that in any iteration $\ell=  0,\ldots,t-1$ of Algorithm \ref{domtoIPalg} the $\DOMtoS(x^{\ell})$ is feasible. We show something stronger. For $\ell=0,\ldots,t-1$ let
	\begin{align*}
	\LP^{(\ell)}&= \{(z,w)\in P\; : \; z\leq x^{(\ell)} \mbox{ and } z_j=x_j^{(\ell)} \mbox{ for } j=1,\ldots,\ell\}, \text{ and}\\
	\IP^{(\ell)}&= \{(z,w)\in \LP^{(\ell)}\; : \; z\in \{0,1\}^n\}.
	\end{align*}
	Notice that if $\LP^{(\ell)}$ is a non-empty set then $\DOMtoS(x^{(\ell)})$ is feasible. We show by induction on $\ell$ that $\LP^{(\ell)}$ and $\IP^{(\ell)}$ are not empty sets for $\ell=0,\ldots,t-1$. First notice that $\LP^{(0)}$ is clearly feasible since by definition $(x^{(0)},y^{(0)})\in \dom(P)$, meaning there exists $(z,w)\in P$ such that $z\leq x^{(0)}$. By Theorem \ref{CV}, there exists $(\tilde{z}^i,\tilde{w}^i) \in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz$. Hence, $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz\leq gx^{(0)}$. So if $x^{(0)}_j=0$, then $ \sum_{i=1}^{k}\theta_i \tilde{z}_j^i =0$, which implies that $\tilde{z}^i_j=0$ for all $i=1,\ldots,k$ and $j= 1,\ldots,n$ where $x^{(0)}_j=0$. Hence, $z^i\leq x^{(0)}$ for $i=1,\ldots,k$. Therefore $(\tilde{z}^i,\tilde{w}^i)\in \IP^{(0)}$ for $i=1,\ldots,k$, which implies $\IP^{(0)}\neq \emptyset$.

	We consider two cases. In the first case, we have $z^*_{\ell+1}=0$. In this case we have $x^{(\ell+1)}_{\ell+1}=0$. Since $z^*\leq x^{(\ell+1)}$, we have $(z^*,w^*)\in \LP^{(\ell+1)}$. Also, $(z^*,w^*)\in P$. By Theorem \ref{CV} there exists $(\tilde{z}^i,\tilde{w}^i)\in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and  $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*$ . We have
	\begin{equation}
	\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*\leq gx^{(\ell+1)}
	\end{equation}
	So for $j\in \{1,\ldots,n\}$ where $x^{(\ell+1)}_j=0$, we have $z^i_j=0$ for $i=1,\ldots,k$. Hence, $\tilde{z}^i\leq x^{(\ell+1)}$ for $i=1,\ldots,k$. Hence, there exists $(z,w)\in S$ such that $z\leq x^{(\ell+1)}$. We claim that $(z,w)\in \IP^{(\ell+1)}$. If $(z,w)\notin \IP^{(\ell+1)}$ we must have $1\leq j \leq \ell$ such that $z_j < x^{(\ell+1)}_{j}$, and thus $z_j = 0$ and $x^{(\ell+1)}_j=1$. Without loss of generality assume $j$ is minimum number satisfying $z_j < x^{(\ell+1)}_{j}$. Consider iteration $j$ of Algorithm \ref{domtoIPalg}. Notice that $z\leq x^{(\ell+1)}\leq x^{(j)}$. We have $x^{(j)}_j=1$ which implies when we solved $\DOMtoS(x^{(j-1)})$ the optimal value was strictly larger than zero. However, $(z,w)$ is a feasible solution to $\DOMtoS(x^{(j-1)})$ and gives an objective value of 0. This is a contradiction, so $(z,w)\in \IP^{(\ell+1)}$.

	Now consider $(x^{(t)},y^{(t)})$. Let $(z,y^{(t)})$ be the optimal solution to $\LP^{(t-1)}$. If $x^{(t)} = 0$, we have $x^{(t)} = z$, which implies that $(x^{(t)},y^{(t)})\in P$, and since $x^{(t)}\in \{0,1\}^n$ we have $(x^{(t)},y^{(t)})\in S$. If $x^{(t)} =1$, it must be the case that $z_t > 0$. By the argument above there is a point $(z',w')\in \IP^{(t-1)}$. We show that $x^{(t)} = z'$. Observe that for $j=1,\ldots,n-1$ we have $z'_j= x_j^{(t-1)}=x_j^{(t)}$. We just need to show that $z'_j = 1$. Assume $z'_j = 0$ for contradiction, then $(z',w')\in \LP^{(t-1)}$ has objective value of $0$ for $\DOMtoS(x^{(t-1)})$, this is a contradiction to $(z,w)$ being the optimal solution.\end{proof}

>>>>

\section{Finding a feasible solution}\label{domTOIP}
Consider a formulation instance $I=(A,G,b)$. Define sets $S(I)$ and $P(I)$ as in (\ref{S'}) and (\ref{P'}), respectively. For simplicity in the notation we denote $P(I),S(I),$ and $g(I)$ with $P$, $S$, and $g$ for this section and the next section. Also, for both sections we assume $t=|\spp(x)|$. Without loss of generality we can assume $x_i = 0$ for $i=t+1,\ldots,n$.

In this section we prove Theorem \ref{domtoIP}. In fact, we prove a stronger result. 
\begin{lemma}\label{domlemma}
	Given $(x,y)\in \dom(P)$, there is an algorithm (the DomToIP algorithm) that finds $(x^{(t)},y^{(t)})\in S$ in polynomial time, such that $x^{t}\leq x$, where $t=|\spp(x)|$\end{lemma}

We prove Lemma \ref{domlemma} by introducing an algorithm that ``fixes" the variables iteratively, starting from $x_1$ and ending at $x_t$. Suppose we run the algorithm for $\ell\in \{0,\ldots,t-1\}$ iterations and we have $(x^{(\ell)},y^{(\ell)})\in \dom(P)$  such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,t$. Now consider the following linear program. The variables of this linear program are the $z\in \bbbr^n$ variables and $w\in \bbbr^p$.
\begin{align}
	\DOMtoS(x^{(\ell)})\quad\quad& \min\quad \;z_{\ell+1}\\
	&\;\text{s.t.} \quad \;\;Az+ Gw\geq b \\
	&\;{\color{white}{\text{s.t.}} }\quad \;\; \; z_j = x^{(\ell)}_j \quad \; j =1,\ldots, \ell\\
	&\;{\color{white}{\text{s.t.}} }\quad \; \;\; z_j \leq x^{(\ell)}_j \quad \; j = \ell+1,\ldots,n\\
	&\;{\color{white}{\text{s.t.}} }\quad \; \;\; z\;\geq 0
\end{align}

If the optimal value to $\DOMtoS(x^{(\ell)})$ is 0, then let $x^{(\ell+1)}_{\ell+1} = 0$. Otherwise if the optimal value is strictly positive let $x^{(\ell+1)}_{\ell+1} = 1$. Let $x^{(\ell+1)}_j = x^{(\ell)}_j$ for $j\in \{1,\ldots,n\}\setminus \{\ell+1\}$.

The above procedure suggests how to find $(x^{(\ell+1)},y^{(\ell+1)})$ from $(x^{(\ell)},y^{(\ell)})$. The DomToIP algorithm initializes with $(x^{(0)},y^{(0)})=(x,y)$ and  iteratively calls this procedure in order to obtain $(x^{(t)},y^{(t)})$. 
\iffalse{
\begin{algorithm}[H]
	\KwIn{$(x,y)\in \dom(S)$}
	\KwOut{$(x^{(t)},y^{(t)}) \in S$, $x^{(t)}\leq x$}
	$x^{(0)}\leftarrow x$\\
	\For{$\ell = 0$ \textbf{to} $t-1$}{
		$x^{(\ell+1)} \leftarrow x^{(\ell)}$\\
		$\eta \leftarrow$ optimal value of $ \DOMtoS(x^{(\ell)})$\\
		$y^{(\ell+1)}\leftarrow$ optimal solution for $w$ variables in $ \DOMtoS(x^{(\ell)})$\\
		\eIf{$\eta = 0$}{
			$x^{(\ell+1)}_{\ell+1} \leftarrow 0$\
		}{
			$x^{(\ell+1)}_{\ell+1} \leftarrow 1$
		}
	}
	\label{domtoIPalg}
	\caption{The DomToIP algorithm}
\end{algorithm}
}\fi
We prove that indeed $(x^{(t)},y^{(t)})\in S$.

	First, we need to show that in any iteration $\ell=  0,\ldots,t-1$ of DomtoIP the $\DOMtoS(x^{\ell})$ is feasible. We show something stronger. For $\ell=0,\ldots,t-1$ let
	\begin{align*}
	\LP^{(\ell)}&= \{(z,w)\in P\; : \; z\leq x^{(\ell)} \mbox{ and } z_j=x_j^{(\ell)} \mbox{ for } j=1,\ldots,\ell\}, \text{ and}\\
	\IP^{(\ell)}&= \{(z,w)\in \LP^{(\ell)}\; : \; z\in \{0,1\}^n\}.
	\end{align*}
	Notice that if $\LP^{(\ell)}$ is a non-empty set then $\DOMtoS(x^{(\ell)})$ is feasible. We show by induction on $\ell$ that $\LP^{(\ell)}$ and $\IP^{(\ell)}$ are not empty sets for $\ell=0,\ldots,t-1$. First notice that $\LP^{(0)}$ is clearly feasible since by definition $(x^{(0)},y^{(0)})\in \dom(P)$, meaning there exists $(z,w)\in P$ such that $z\leq x^{(0)}$. By Theorem \ref{CV}, there exists $(\tilde{z}^i,\tilde{w}^i) \in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz$. Hence, $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz\leq gx^{(0)}$. So if $x^{(0)}_j=0$, then $ \sum_{i=1}^{k}\theta_i \tilde{z}_j^i =0$, which implies that $\tilde{z}^i_j=0$ for all $i=1,\ldots,k$ and $j= 1,\ldots,n$ where $x^{(0)}_j=0$. Hence, $z^i\leq x^{(0)}$ for $i=1,\ldots,k$. Therefore $(\tilde{z}^i,\tilde{w}^i)\in \IP^{(0)}$ for $i=1,\ldots,k$, which implies $\IP^{(0)}\neq \emptyset$.

	We consider two cases. In the first case, we have $z^*_{\ell+1}=0$. In this case we have $x^{(\ell+1)}_{\ell+1}=0$. Since $z^*\leq x^{(\ell+1)}$, we have $(z^*,w^*)\in \LP^{(\ell+1)}$. Also, $(z^*,w^*)\in P$. By Theorem \ref{CV} there exists $(\tilde{z}^i,\tilde{w}^i)\in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and  $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*$ . We have
	\begin{equation}
	\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*\leq gx^{(\ell+1)}
	\end{equation}
	So for $j\in \{1,\ldots,n\}$ where $x^{(\ell+1)}_j=0$, we have $z^i_j=0$ for $i=1,\ldots,k$. Hence, $\tilde{z}^i\leq x^{(\ell+1)}$ for $i=1,\ldots,k$. Hence, there exists $(z,w)\in S$ such that $z\leq x^{(\ell+1)}$. We claim that $(z,w)\in \IP^{(\ell+1)}$. If $(z,w)\notin \IP^{(\ell+1)}$ we must have $1\leq j \leq \ell$ such that $z_j < x^{(\ell+1)}_{j}$, and thus $z_j = 0$ and $x^{(\ell+1)}_j=1$. Without loss of generality assume $j$ is minimum number satisfying $z_j < x^{(\ell+1)}_{j}$. Consider iteration $j$ of the DomToIP algorithm. Notice that $z\leq x^{(\ell+1)}\leq x^{(j)}$. We have $x^{(j)}_j=1$ which implies when we solved $\DOMtoS(x^{(j-1)})$ the optimal value was strictly larger than zero. However, $(z,w)$ is a feasible solution to $\DOMtoS(x^{(j-1)})$ and gives an objective value of 0. This is a contradiction, so $(z,w)\in \IP^{(\ell+1)}$.

	Now consider $(x^{(t)},y^{(t)})$. Let $(z,y^{(t)})$ be the optimal solution to $\LP^{(t-1)}$. If $x^{(t)} = 0$, we have $x^{(t)} = z$, which implies that $(x^{(t)},y^{(t)})\in P$, and since $x^{(t)}\in \{0,1\}^n$ we have $(x^{(t)},y^{(t)})\in S$. If $x^{(t)} =1$, it must be the case that $z_t > 0$. By the argument above there is a point $(z',w')\in \IP^{(t-1)}$. We show that $x^{(t)} = z'$. Observe that for $j=1,\ldots,n-1$ we have $z'_j= x_j^{(t-1)}=x_j^{(t)}$. We just need to show that $z'_j = 1$. Assume $z'_j = 0$ for contradiction, then $(z',w')\in \LP^{(t-1)}$ has objective value of $0$ for $\DOMtoS(x^{(t-1)})$, this is a contradiction to $(z,w)$ being the optimal solution. This concludes the proof of Lemma \ref{domlemma}.

	Notice that Lemma \ref{domlemma} implies Theorem \ref{domtoIP}, since it is easy to obtain an integer point in $\dom(P)$: rounding up any fractional point in $P$ gives us a point in $\dom(P)$.

@@

Assume we are given a point $(x^*,y^*)\in P$. For instance, $(x^*,y^*)$ can be the optimal solution of minimizing a cost function $cx$ over set $P$, which provides a lower bound on $\min_{(x,y)\in S(I)} cx$.  In this section, we prove Theorem \ref{binaryFDT} by describing the Fractional Decomposition Tree (FDT) algorithm.
\iffalse{We also remark that if $g_I=1$, then the algorithm will give an exact decomposition of any feasible solution. }\fi

The FDT algorithm grows a tree similar to the classic branch-and-bound search tree for integer programs. Each node represents a partially integral vector $(\bar{x},\bar{y})$ in $\dom(P)$ together with a multiplier $\bar{\lambda}$. The solutions contained in the nodes of the tree become progressively more integral at each level. In each level of the tree, the algorithm maintain a conic combination of points with the properties mentioned above. Leaves of the FDT tree contain solutions with integer values for all the $x$ variables that dominate a point in $P$. We will later see how we can turn these into points in $S$.

\paragraph{Branching on a node}
We begin with the following lemmas that show how the FDT algorithm branches on a variable.
\begin{lemma}\label{LPClemma}
	Given $(x',y')\in \dom(P)$ and $\ell\in \{1,\ldots,n\}$, we can find in polynomial time vectors $(\hat{x}^0,\hat{y}^0),(\hat{x}^1,\hat{y}^1)$ and scalars $\gamma_0,\gamma_1 \in [0,1]$ such that: (i) $\gamma_0 + \gamma_1  \geq \frac{ 1}{g}$, (ii) $(\hat{x}^0,\hat{y}^0)$ and $(\hat{x}^1,\hat{y}^1)$ are in  $ P$
		,(iii) $\hat{x}^0_\ell=0$ and $\hat{x}^1_\ell=1$, (iv) $\gamma_0 \hat{x}^0 + \gamma_1\hat{x}^1 \leq x'$.
\end{lemma}

@@

\paragraph{Growing and Pruning FDT tree} The FDT algorithm maintains nodes $L_i$ in iteration $i$ of the algorithm. The nodes in $L_i$ correspond to the nodes in level $L_i$ of the FDT tree. The points in the leaves of the FDT tree, $L_t$, are points in $\dom(P)$ and are integral for all integer variables.

@@

	Notice that $\theta = \gamma$ is in fact a feasible solution to $\prun(L')$. Let $\theta^*$ be the optimal vertex point solution to this LP. Since the problem is in $\bbbr^{2k}$,  $\theta^*$ has to satisfy $2k$ linearly independent constraints at equality. However, there are only $t$ constraints of type (\ref{packs}). Therefore, there are at most $t$ coordinates of $\theta^*_j$ that are non-zero. We claim that $L_{i+1}$ which consists of $(x^j,y^j)$ for $j=1,\ldots,2k$ and their corresponding multipliers $\theta^*_j$ satisfy the properties in the statement of the lemma. Notice that, we can discard the nodes in $L_{i+1}$ that have $\theta^*_j=0$, so $|L_{i+1}| \leq t$. Also, since $\theta^*$ is optimal and $\gamma$ is feasible for $\prun(L')$, we have $\sum_{j=1}^{k} \theta^*_j \geq \sum_{j=1}^{2k}\gamma_j \geq \frac{1}{g^{i+1}}$. 
\end{proof}
\paragraph{From leaves of FDT to feasible solutions}
The leaves of the FDT tree,  $L_t$, have the property that every solution $(x,y)$ in $L_t$ has $x\in\{0,1\}^n$ and $(x,y)\in \dom(P)$. By applying Lemma \ref{domlemma} we can obtain a point $(x',y')\in S$ such that $x'\leq x$. This conclude the description of the FDT algorithm and proves Theorem \ref{binaryFDT}.
